Raft Distributed Consensus Algorithm over WebRTC (Web Real-Time Communication)

### 2015-09-16 research_class/paper.tex
Fix grammar; remove extra "the".

One limitation of the Raft protocol is that the if the cluster
membership drops from two nodes to one node then the cluster will
become unavailable without manual intervention. This is because when
there are two nodes in the cluster, both nodes are required for for
a majority vote and when one member is forcible shutdown then the
remaining cluster node will be unable to win elections or even commit
transaction entries and the cluster will become unavailable. There are
several options to get around this problem:

>>>>

One limitation of the Raft protocol is that if the cluster
membership drops from two nodes to one node then the cluster will
become unavailable without manual intervention. This is because when
there are two nodes in the cluster, both nodes are required for for
a majority vote and when one member is forcible shutdown then the
remaining cluster node will be unable to win elections or even commit
transaction entries and the cluster will become unavailable. There are
several options to get around this problem:
